---
title: "Assignment Data Science 2"
---

# Task

This blog post's goal is to predict a classification of social media text messages whether they contain hate speech or not. 
In the beginning, there will be explorative data analysis, followed by machine learning with Tidymodels and a neural network computation via Hugging Face. 


# Data and packages


```{r}
d_raw <- read.csv("d_hate.csv", sep = ",")
```


Packages: 

```{r message=FALSE}
library(tidyverse)
library(easystats)
library(tidymodels)
library(tidytext)  # Textmining
library(textrecipes)  # Text analysis in tidymodels recipes
library(lsa)  # stopwords
library(discrim)  # naive bayes classification
library(naivebayes)
library(tictoc)  # Zeitmessung
library(fastrtext)  # Word embeddings
library(remoji)  # Emojis
library(tokenizers)  # tokenize vecotrs
library(syuzhet)
library(pradadata)
```


To speed up computations later on, I activate parallel computing (where possible).

```{r}
library(parallel)
all_cores <- detectCores(logical = FALSE)

library(doFuture)
registerDoFuture()
cl <- makeCluster(3)
plan(cluster, workers = cl)
```

Stopwords: 

```{r}
stop1 <- tibble(word = quanteda::stopwords("english"))
```


Sentiment Analysis: 

```{r}
afinn <- get_sentiments("afinn")
```


Wild emojis:

```{r}
data("wild_emojis")
```



```{r}
conflicted::conflict_prefer("select", "dplyr")

conflicted::conflict_prefer("filter", "dplyr")
```



# EDA

Now let's take a deeper look into the whole dataset, before splitting it up! 

## Data Descriptions

```{r}
d_raw %>% 
  count(class)
```

Roughly 1/4 of the 5593 observations are classified as hate speech. 

```{r}
d_hate <-   
  d_raw %>% 
  mutate(text_length = str_length(tweet)) 


d_hate %>% 
  summarise(mean(text_length), max(text_length), min(text_length))
```

There is quite a gap between the shortest and the longest tweet! I would love to see text_length visually for all tweets though:

```{r}
d_hate %>% 
  ggplot()+
  aes(x = text_length)+
  geom_density()+
  theme_minimal()
```
Only a rare number of tweets has more than 200 strings. 


## Most frequent words

```{r}
d_long <- 
  d_hate %>% 
  unnest_tokens(input = tweet, output = token)
```


```{r}
long2 <- 
  d_long %>% 
  rename(word = token) %>% 
  anti_join(stop1)
```

```{r}
words <- long2 %>% 
  dplyr::filter(str_detect(word, "[A-Za-z]")) %>% 
  count(word, sort = TRUE)
```


```{r}
library(wordcloud)

wordcloud(words = words$word, freq = words$n, max.words = 100, random.color = FALSE, colors = brewer.pal(8, "Dark2"))
```
Well, there are quite a few negative (even insulting) words in there... But I love that Oreo is among the most frequent words! Who doesn't like a chocolate cookie every now and then?

Out of curiosity, let me check what "rt" stands for: re-tweet. Makes sense, but also means, that I can add that to the list of stopwords! Together with "http" and "t.co" (just indicates that they link a website).

Also, "amp" stands for: any means possible :)


## Sentiment analysis: How positive/negative is our data?


```{r}
tic()
senti1 <- get_nrc_sentiment(d_hate$tweet, language = "english")
toc()
```

```{r}
senti1_results <- 
  senti1 %>% 
  summarise(across(.cols = everything(), .fns = sum))

head(senti1_results)
```


I love images, so here we go: 

```{r}
piechart_data <-
  senti1_results %>% 
  dplyr::select(-positive, -negative) %>% 
  pivot_longer(cols = anger:trust) %>% 
  arrange(desc(name)) 

piechart_data %>% 
  ggplot()+
  aes(x = "", y = value, fill = name)+
  geom_bar(stat = "identity", width = 1)+
  coord_polar("y", start = 0)+
  theme_void()+
  scale_fill_brewer(palette="Set3")+
  guides(fill = guide_legend(title = "Emotion"))+
  geom_text(aes(label = name), position = position_stack(vjust = 0.5))+
  theme(legend.position = "none")
```



Share of negative feelings: 

```{r}
senti1 %>% 
  summarise(anger_prop = 1565/4208,
            disgust_prop = 2297/4208,
            fear_prop = 1768/4208,
            sadness_prop = 2464/4208)
```

Several of the words seem to be associated with more than one negative emotion.

Share of positive feelings:

```{r}
senti1 %>% 
  summarise(anticipation_prop = 1824/3240,
            joy_prop = 1753/3240,
            surprise_prop = 860/3240,
            trust_prop = 2099/3240)
```


I must admit that I am surprised of the high numbers of negative feelings compared to the rather small share of tweets categorized as "hate". It seems as if many tweets were negative, but maybe not hate?


## Insults

Props to https://www.insult.wiki/list-of-insults for sharing a list free to use!
I copied the words into excel to easily import them to R Studio!

```{r}
library(readxl)
insults <- read_excel("/Users/chrissi/Documents/Studium/Module/Data Science/DS 2/Prüfung/Insults_English.xlsx", col_names = FALSE)

insults$value <- 1

insults <- insults %>% 
  rename(word = "...1")

head(insults)
```

Let's see how many insults from my list are included in the data!

```{r}
d_long %>% 
  mutate(ins_yes = if_else(token %in% insults$word, 1, 0)) %>% 
  count(ins_yes)
```

Alright, we have 2508 hits on insults! That might help the prediction.




## Emojis

Here is a dataframe containing several wild emojis as another possible predictor. Let's check how many there are! 

```{r}
d_emojis <- 
  train2 %>% 
  select(id, text) %>% 
  mutate(wild_emoji = text %in% wild_emojis$emoji)


```

```{r}
d_long %>% 
  mutate(wildemo_yes = if_else(token %in% wild_emojis$emoji, 1, 0)) %>% 
  count(wildemo_yes)
```

No emoji from that list is to be found in our data. Consequently, we can leave that step out of the recipe


# Preparation for Machine Learning

Now that I have a rough understanding of my dataset, I am excited to get into the Machine Learning part - but first things first. 


```{r}
d_split <- initial_split(d_raw, strata = class, prop = .7)

d_train <- training(d_split)

d_test <- testing(d_split)
```


```{r}
train2 <- 
  d_raw %>% 
  select(-id) %>% 
  mutate(id = 1:nrow(.)) %>% 
  select(id, everything()) %>% 
  rename(text = tweet) %>% 
  mutate(as.factor(text))
```



```{r}
stop2 <- 
  stop1 %>% 
  add_row(word = "rt") %>% 
  add_row(word = "http") %>%
  add_row(word = "t.co")
```


## Adding word embedding data 

https://wikipedia2vec.github.io/wikipedia2vec/pretrained/ 

Als Arrow-Datei speichern

```{r}
wiki_de_embeds_path <- "/Users/chrissi/Dokumente/Angewandte Wirtschafts- und Medienpsychologie/WS 2023:24/Data Science 2/Wiki2Vec_German.txt"

wiki_de_embeds <-
  data.table::fread(file = wiki_de_embeds_path,
                    sep = " ",
                    header = FALSE,
                    showProgress = FALSE)
```

```{r}
names(wiki_de_embeds)[1] <- "word"

wiki <- as_tibble(wiki_de_embeds)
```



# Machine Learning

## get_sentiment

R does not tolerate the command `get_sentiment` within a `step_mutate` today, so I'll do that outside of the recipe and add the new predictors into the training data set. Error messages varied a lot, depending on what I had tried, but fitting never worked out. Therefore, I'll now work around this problem.


```{r}
train3 <- 
  train2 %>% 
  mutate(
    n_insult = syuzhet::get_sentiment(text, method = "custom", lexicon = sentiws),
    rsenti = syuzhet::get_sentiment(text, method = "custom", lexicon = afinn))
```

## Cross-validation

```{r}
set.seed(42)
folds <- vfold_cv(train3, v = 5, repeats = 1)
```


## Recipe


```{r}
rec1 <- 
  recipe(class ~ ., data = train3) %>% 
  update_role(id, new_role = "id")  %>% 
  step_regex(input = text, pattern = "[a-zA-Z]+") %>% 
  step_tokenize(text) %>%
  step_stopwords(text, keep = FALSE, custom_stopword_source = stop2) %>%
  #step_word_embeddings(text, embeddings = wiki, aggregation = "mean") %>%  
  step_nzv() %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_untokenize(text) #Naive Bayes cannot deal with textrecipes_tokenlist
```


```{r}
rec2 <- 
  recipe(class ~ ., data = train3) %>% 
  update_role(id, new_role = "id")  %>% 
  step_regex(input = text, pattern = "[a-zA-Z]+") %>% 
  step_tokenize(text) %>%
  step_stopwords(text, keep = FALSE, custom_stopword_source = stop2) %>%
  #step_word_embeddings(text, embeddings = wiki, aggregation = "mean") %>%  
  step_nzv() %>% 
  step_normalize(all_numeric_predictors()) 
```

```{r}
rec1_prep <- prep(rec1, train3)

rec1_bake <- bake(rec1_prep, new_data = NULL)

head(rec1_bake)
```



## Naive Bayes

```{r}
nb_modell <- naive_Bayes() %>%
  set_mode("classification") %>%
  set_engine("naivebayes")

wf1 <-
  workflow() %>% 
  add_recipe(rec1) %>% 
  add_model(nb_modell)

tic()
fit1 <-
  fit_resamples(
    wf1,
    folds,
    control = control_resamples(save_pred = TRUE)
  )
toc()
```

```{r}
wf1_performance <-
  collect_metrics(fit1)

wf1_performance
```


## Random Forest

```{r}
rf_model <- 
  rand_forest(mtry = 3,
              min_n = tune(),
              trees = 1000) %>% 
  set_engine("ranger") %>% 
  set_mode("classification")

rf_wf <- 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(rec2)

rf_grid <- 
  grid_regular(min_n(), levels = 1)

tic()
rf_fit <- 
  tune_grid(object = rf_wf, resamples = folds, grid = rf_grid)
toc()

show_best(rf_fit)
```


# Predictions 

final_hate <-
  last_fit(wf, data_split)
  


## Metrics

final_hate %>% collect_metrics()

autoplot

# Neural Networks

## Hugging Face API



## Own neural network

import os
import numpy as np
import pandas as pd

import tensorflow as tf
import tensorflow_hub as hub
from tensorflow.keras.models import Sequential
from tensorflow.keras.layers import Dense
from sklearn.metrics import accuracy_score


Daten laden


tf.config.list_physical_devices('GPU')
print("GPU is", "available" if tf.config.list_physical_devices("GPU") else "NOT AVAILABLE")


embedding = "https://tfhub.dev/google/nnlm-de-dim50/2"
hub_layer = hub.KerasLayer(embedding, input_shape=[],
                           dtype=tf.string, trainable=True)

Link ausbessern!! Deutsche Embeddings


Modell: 

model = tf.keras.Sequential()
model.add(hub_layer)
model.add(tf.keras.layers.Dense(20, activation='relu'))
model.add(tf.keras.layers.Dense(10, activation = 'relu'))
model.add(tf.keras.layers.Dense(1))

model.summary()


model.compile(optimizer='adam',
              loss=tf.keras.losses.BinaryCrossentropy(from_logits=True),
              metrics=['accuracy'])


Modell trainieren:

model.fit(X_train, y_train,
epochs=4,
batch_size=32,
validation_data=(X_test, y_test),
verbose = 1)

Modell testen:

y_pred = (model.predict(X_test) > 0.5).astype("int32")
accuracy = accuracy_score(y_test, y_pred)
print(f"Test Accuracy: {accuracy}")